---
title: 'Case Study 3 : Give Your Visualizations Wings to Fly'
author: "Exode"
date: "5/9/2020"
output: html_document
---
```{r, include = FALSE}
library(car)
library(mosaic)
library(pander)
library(scatterplot3d)
library(plotly)
library(ggplot2)
library(tidyverse)
library(DT)
library(broom)
library(ourworldindata)
library(nycflights13)
```
```{r include=FALSE}
glimpse(flights)
```
```{r include=FALSE}
fligh <- subset(flights,dep_time <= 1200&origin=="JFK"| origin=="LGA"|origin=="EWR"&dep_delay<=quantile(dep_delay,0.75,na.rm=TRUE))
glimpse(fligh)
```
```{r include=FALSE}
fli<-fligh %>% group_by(carrier,origin) %>% summarise(q3 = quantile(dep_delay,0.75,na.rm=TRUE))
```

## Background

The data was tried from the nycflights13::flights dataset that contains information about flights that departed JFK, LGA, or EWR in 2013. We are going to use the data to answer a few questions. We will try which airline have the least departure delay time and which airport one should fly from if they don't want to arrive to their destination with a huge delay.
```{r}
flig <- fli %>% group_by(carrier,origin) %>% summarise(delay=min(q3))
```


##Questions


**Question1: If I am leaving before noon, which two airlines do you recommend at each airport (JFK, LGA, EWR) that will have the lowest delay time at the 75th percentile?**

```{r}
K <- flig %>% ggplot(aes(x=reorder(carrier,desc(delay)),y=delay,color=carrier))+geom_point()+facet_wrap(~origin,nrow=3)+labs(title="Airlines with the Lowest Delay Time at the 75th Percentile",x="Carrier",y="Delay")+geom_col()+theme_dark()

ggplotly(K, tooltip=c("carrier","delay"))
```
```{r}
ggsave("plot1.png")
```

*Thus, if one is flying from EWR, I would recommend VX and DL because they have the lowest departure delay time at the 75th percentile.*


*Thus, if one is flying from JFK, I would recommend MK and AA because they have the lowest departure delay time at the 75th percentile.*

*Thus, if one is flying from EWR, I would recommend US and 00 because they have the lowest departure delay time at the 75th percentile.*

```{r include=FALSE}
pander(flights %>% group_by(carrier,origin) %>% summarise(q3=quantile(dep_delay,0.75,na.rm=TRUE)))
```
```{r}
f <- subset(flights, carrier=="DL")
```
```{r}
fi <- f %>% group_by(carrier,origin) %>% summarise(arrival_delay=min(arr_delay,na.rm=TRUE))
```

**Question2: Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airlines?**

```{r}

K <- fi %>% ggplot(aes(x=reorder(origin,desc(arrival_delay)),y=arrival_delay,size=arrival_delay,color=origin))+geom_point()+labs(y="Minimun Arrival Delay in Minutes",x="carrier",title="Best Airport to Fly From in Order to Minimize\n Arrival Delay Time When Flying With Delta Airlines")+ theme(plot.title = element_text(hjust = .5))

ggplotly(K, tooltip=c("origin","arrival_delay"))
```
```{r}
ggsave("plot2.png")
```

**To minimize the day arrival delay, one should fly from JFK if they are flying with Delta airlines**
